---
title: 'Data Visualization: Bad Drivers Data'
author: "Sowmya"
date: "2022-09-23"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

# Data Importation

<br>

```{r}
#Importing Data and creating overview 
data <- read.csv(("https://raw.githubusercontent.com/fivethirtyeight/data/master/bad-drivers/bad-drivers.csv"))
head(data)
```

<br>

# Data Cleaning and Summary

<br>

```{r}
sum(is.na(data)) #check for NA
colnames(data) #get column names

#changing column names
colnames(data) <-
  c("State","Fatal_collisions", "Percentage_speeding","percentage_alcohol_impared", "Percentage_no_distracted", "percentage_with_no_prior_accidents", "Car_Insurance_Premiums", "Losses_to_insurance_companies_per_driver") 
colnames(data)

#Getting Summary
summary(data)

```
<br>

# Density Plot

<br>

The plot below in Fig 1 gives the density plot of the Fatal Collisions variable from the data. From the density plot, we observe that the data on the Fatal collisions is reasonably normally distributed.


```{r, fig.cap="Fig 1"}
#Loading ggplot package
library(ggplot2)

#Plotting the density plot for the Fatal Collisions
ggplot(data) +
  aes(x = Fatal_collisions) +
  geom_density(adjust = 1L, fill = "#B22222") +
  labs(title = "Fatal Collisions", subtitle = "Density Plot") +
  theme_minimal()
```

<br>

# Scatterplot

<br>

The plot below in Fig 2 gives the scatterplot of the Percentage Alcohol Impaired for the driver against the Fatal Collisions. The scatterplot shows that there is no linear relationship between Percentage Alcohol Impaired and Fatal Collision.

```{r, fig.cap="Fig 2"}
#Plotting the Scatterplot for Percentage Alcohol Impaired against Fatal Collisions
ggplot(data) +
  aes(x = percentage_alcohol_impared, y = Fatal_collisions) +
  geom_point(shape = "circle", size = 1.5, colour = "#4682B4") +
  labs(
    title = "Percentage Alcohol Impaired vs Fatal Collisions",
    subtitle = "Scatterplot"
  ) +
  theme_minimal()
```



